\systemnamenospace: Head Orientation-Based Selection\\in Physical Spaces

### 2014-08-14 doc/sui14/iteration2.tex
updated description of figure 9, this leads to page overflow, so removed \newpage from iteration 3

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/IRIntensityDistribution.pdf}
\caption{\changes{Empirical measurement of IR intensity at different positions. We measure the intensity on a horizontal plane at one-meter intervals from the IR emitter.} On that plane, a sample is taken every 5 centimeters, \changes{and we stop when the reading is smaller than ambient noise.} \changes{To match our assumption about the relationship between angles and intensities, the vertical axis is changed to the degree of the angle.} The size and color brightness represent the intensity of the readings for visualization.}
\label{fig:measurement}
\end{figure}

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=0.95\columnwidth]{figures/IRIntensityDistribution.pdf}
\caption{\changes{Empirical measurement of IR intensity at different positions. We measure the intensity on a horizontal plane at one-meter intervals from the IR emitter.} On that plane, a sample is taken every 5 centimeters, \changes{and we stop when the intensity reading is around the level of ambient noise. To match our assumption about the relationship between angles and intensities, the vertical axis shows the relative degree of the angle rather than the distance to the center of the plane.} The size and color brightness represent the intensity of the readings for visualization.}
\label{fig:measurement}
\end{figure}
